\documentclass[12pt]{article}
\usepackage{fullpage,enumitem,amsmath,amssymb,graphicx, listings, array}

\begin{document}

\begin{center}
{\Large CS221 Fall 2018 - 2019 Homework 3}

\begin{tabular}{rl}     
Name: & Dat Nguyen \\
Date: & 2/12/2019
\end{tabular}
\end{center}
 
 By turning in this assignment, I agree by the Stanford honor code and declare
that all of this is my own work.

\section*{Problem 1: word segmentation}
\begin{enumerate}[label=(\alph*)]
    \item
    Query string: "Therearecountlessanimalsonearth". \\
    Correct segmentation: "There are countless animals on earth". \\
    Wrong segmentation: "There are count less animals on earth". \\
    Where 1-gram and c("count") = 0.1, c("less") = 0.2 and c("countless") = 0.2 
\end{enumerate}

\section*{Problem 2: vowel insertion}
\begin{enumerate}[label=(\alph*)]
    \item
    Query string: "th bs r n \ btfl flwr" \\
    Correct vowel insertion: "the bees are on a beautiful flower". \\
    Wrong vowel insertion: "the books are on a beautiful flower". \\
    Where bigramCost('the', 'bees') = 0.2, bigramCost('bees', 'are') = 0.1, 
    bigramCost('the', 'books') = 0.1, and bigramCost('books', 'are') = 0.3.
\end{enumerate}

\section*{Problem 3: putting it together}
\begin{enumerate}[label=(\alph*)]
    \item \addtocounter{enumi}{1}
    \begin{itemize}
    \item States: list of actions made in each step, where each action includes 2 kinds of information: next index to insert space after that in the query string and the choosen word based on the substring between most recent 2 spaces of the query string. \\
    \item Actions: as explained above.\\
    \item Cost: the bigram cost of the previous choosen word and the currently choosen word. \\
    \item Initial state: empty list. \\
    \item End state: if the next index to insert space after that is the last index of the query string.
	\end{itemize}

    \item
    We define $u_b(w) = \underset{w' \in Vocabulary}{min}b(w', w)$, and the following relaxed problem. \\
    \begin{itemize}
    \item States: like the original problem. \\
    \item Actions: like the original problem. \\
    \item Cost: let sb be substring between most recent 2 spaces of the query string resulting from state s and action a. We define the cost to be $Cost_{rel}(s, a) = \underset{st \in possibleFills(sb)}{\text{min}}u_b(st)$. \\
    \item Start state: like original problem. \\
    \item End state: like original problem.
    \end{itemize}
    Next we will prove that $Cost_{rel}(s, a) \leq Cost(s, a)$. Let sb be substring between most recent 2 spaces of the query string and st' be the choosen word from possibleFills(sb) resulting from state s and action a. We have
    \begin{align*}
    	Cost_{rel}(s, a) &= \underset{st \in possibleFills(sb)}{\text{min}}u_b(st) \\
    	&\leq u_b(st') \\
    	&= \underset{w' \in Vocabulary}{min}b(w', st') \\
    	&\leq b(\text{prevWord}, st') \\
    	&= Cost(s, a) 
    \end{align*}
    Therefore if we let $h(s) = FutureCost_{rel}(s)$ then $h(s)$ is consistent. Since the cost for the relaxed problem are all equal for choosen words given substring between most recent 2 spaces of the query string, we can cosider the following problem to save computation. 
    \begin{itemize}
    \item States: list of next index to insert space after that in the query string \\
    \item Actions: next index to insert space after that in the query string \\
    \item Cost: let sb be substring between most recent 2 spaces of the query string resulting from state s and action a. We define the cost to be $Cost_{rel}(s, a) = \underset{st \in possibleFills(sb)}{\text{min}}u_b(st)$. \\
    \item Start state: empty list. \\
    \item End state: if the next index to insert space after that is the last index of the query string.
    \end{itemize}
    And when doing in the original problem we let $FutureCost(s, a)$ be the future cost in the relaxed problem starting from the current substring in the query string being considered by the original problem.

    \item
    UCS is a special case of $A^*$ if we let $h(s) = 0$. \\
    BFS is a special case of UCS if we let every edge have cost = 1.
\end{enumerate}
\end{document}